---
title: "Confirmatory 1A Analysis Markdown"
output:
  html_document: default
  word_document: default
---
# PREPARATION

## Load Packages
```{r message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(janitor)
library(grid)
library(cowplot)
library(httr)
library(extrafont)
library(here)
library(ggeasy)
library(rstatix)
library(apa)
library(ez)
library(afex)
library(papaja)
library(patchwork)
library(jmv)
library(report)
```

## Read in data
```{r message=FALSE, warning=FALSE, include=FALSE}
options(scipen=999) # remove scientific notation

data1A <- read_csv(here("data_files", "scored_master_dataset_1A.csv"))
```

## First factor: Subfield
```{r echo=FALSE}
# first, let's collapse the subfields into 4 main groups: developmental, cognition, social and 'other'
subfield_groups <- data1A %>%
  mutate(subfield_groups = case_when(subfield == "Behavioural Neuroscience" ~ "Other",
                                     subfield == "Cognitive Neuroscience" ~ "Other",
                                     subfield == "Health Psychology" ~ "Other",
                                     subfield == "Perception" ~ "Other",
                                     subfield == "Developmental Psychology" ~ "Development",
                                     subfield == "Social Psychology" ~  "Social",
                                     TRUE ~ as.character(subfield))) %>%
  relocate(subfield_groups, .after = subfield)

# we can now delete the original subfield column
subfield_groups <- subfield_groups %>%
  select(-subfield)

# Subfield summary

subfield_summary <- subfield_groups %>%
    count(subfield_groups) 

subfield_summary
```

## Second factor: Time 

```{r echo=FALSE}
# we want to group the data in 3 six months: first half of 2014, second half of 2014 and first half of 2015

dates <- subfield_groups %>%
  mutate(time_period = case_when(
    str_detect(article_id_number, "1-2014|2-2014|3-2014|4-2014|5-2014|6-2014") ~ "1st half 2014",
    str_detect(article_id_number, "7-2014|8-2014|9-2014|10-2014|11-2014|12-2014") ~ "2nd half 2014",
    str_detect(article_id_number, "1-2015|2-2015|3-2015|4-2015|5-2015") ~ "1st half 2015")) %>%
  relocate(time_period, .after = article_id_number)

# Timeperiod summary

timeperiod_summary <- dates %>%
  count(time_period)

timeperiod_summary

```

## Select relevant data 

```{r message=FALSE, include=FALSE}
final1A <- dates %>%
  select(article_id_number, subfield_groups, time_period, total_data_score, total_materials_score)

# make sure subfield and timeperiod are factors 

final1A$subfield_groups <- fct_relevel(final1A$subfield_groups, c("Development", "Social", "Cognition", "Other"))
final1A$time_period <- fct_relevel(final1A$time_period, c("1st half 2014", "2nd half 2014", "1st half 2015"))

# check data types

glimpse(final1A)
```

# DATA ANOVA Analysis 

```{r echo=FALSE}
# We decided to use Type II ANOVA tests because this appears to be the more conservative test out of Type I, II and III tests, and is most appropriate for our findings

data_ANOVA <- final1A %>%
  anova_test(total_data_score ~ subfield_groups * time_period)

data_ANOVA

```

Our two-way between-subjects ANOVA generated a significant main effect of time period, F(`r data_ANOVA$DFn[2]`, `r data_ANOVA$DFd[2]`) = `r data_ANOVA$F[2]`, p = `r data_ANOVA$p[2]`, ges = `r data_ANOVA$ges[2]`. However, the main effect of subfield, F(`r data_ANOVA$DFn[1]`, `r data_ANOVA$DFd[1]`) = `r data_ANOVA$F[1]`, p = `r data_ANOVA$p[1]`, ges = `r data_ANOVA$ges[1]`, and the interaction between subfield and time period, F(`r data_ANOVA$DFn[3]`, `r data_ANOVA$DFd[3]`) = `r data_ANOVA$F[3]`, ges = `r data_ANOVA$ges[3]`, were not statistically significant.

  
```{r echo=FALSE}
# Alternatively we can use the papaja package to print the stats: 

data_aov <- aov_ez(
  data = final1A, dv = "total_data_score", 
  id = "article_id_number", 
  between = c("time_period", "subfield_groups"), 
  type = "2")

data_aov$anova_table

data_apa <- apa_print(data_aov)

apa_table(data_apa$table,
          caption = "Between-subjects ANOVA for Open Data Scores", 
          note = "This table was created with apa_table().")
```

Our two-way between-subjects ANOVA generated a significant main effect of time period, `r data_apa$full$time_period`. However, the main effect of subfield, `r data_apa$full$subfield_groups`, and the interaction between time period and subfield, `r data_apa$full$time_period_subfield_groups`, were not statistically significant. 

# MATERIALS ANOVA Analysis 

```{r echo=FALSE}
materials_ANOVA <- final1A %>%
  anova_test(total_materials_score ~ subfield_groups * time_period)

materials_ANOVA
```

Our two-way between-subjects ANOVA generated a significant main effect of subfield, F(`r materials_ANOVA$DFn[1]`, `r materials_ANOVA$DFd[1]`) = `r materials_ANOVA$F[1]`, p = `r materials_ANOVA$p[1]`, ges = `r materials_ANOVA$ges[1]`, and a significant main effect of time period, F(`r materials_ANOVA$DFn[2]`, `r materials_ANOVA$DFd[2]`) = `r materials_ANOVA$F[2]`, p = `r materials_ANOVA$p[2]`, ges = `r materials_ANOVA$ges[2]`. However, the interaction between subfield and time period, F(`r materials_ANOVA$DFn[3]`, `r materials_ANOVA$DFd[3]`) = `r materials_ANOVA$F[3]`, ges = `r materials_ANOVA$ges[3]`, was not statistically significant.

  
```{r echo=FALSE}
# Alternatively we can use the papaja package to print the stats: 

materials_aov <- aov_ez(
  data = final1A, dv = "total_materials_score", 
  id = "article_id_number", 
  between = c("time_period", "subfield_groups"), 
  type = "2")

materials_aov$anova_table

materials_apa <- apa_print(materials_aov)

apa_table(materials_apa$table,
          caption = "Between-subjects ANOVA for Open Materials Scores", 
          note = "This table was created with apa_table().")
```

Our two-way between-subjects ANOVA generated a significant main effect of subfield, `r materials_apa$full$subfield_groups`, and a significant main effect of time period, `r materials_apa$full$time_period`. However the interaction between time period and subfield, `r materials_apa$full$time_period_subfield_groups`, was not statistically significant. 

# PLOTS

## DATA

### Subfield x Data Score

```{r echo=FALSE}
data_subfield_descriptives <- final1A %>%
  group_by(subfield_groups) %>%
  summarise(mean_data_score = mean(total_data_score, na.rm = TRUE),
            SD = sd(total_data_score, na.rm = TRUE),
            N = n(),
            stderr = SD/sqrt(N))

data_subfield_descriptives

# let's plot this

d1 <- data_subfield_descriptives %>%
  ggplot(aes(x = subfield_groups, y = mean_data_score, fill = subfield_groups)) +
  geom_col() +
  geom_errorbar(aes(ymin = mean_data_score - stderr, ymax = mean_data_score + stderr), # specifying what the standard error is
                size=.3, # thinner lines
                width=.2) + # narrower bars
    theme_classic() +
    scale_fill_manual(values=c("#EC407A","#42A5F5", "#FFCC33", "#00CC99")) +
  scale_y_continuous(limits = c(0,25), expand = c(0,0)) + # getting the bars to start at the bottom of the graph
  easy_remove_legend() +
  easy_all_text_size(size = 8) + # change the size of the text
  easy_labs(x = "Subfield", y = "Mean Open Data Score") + # change the x and y labels
  ggtitle('(a)')

```

### Time Period x Data Score

```{r echo=FALSE}
data_timeperiod_descriptives <- final1A %>%
  group_by(time_period) %>%
  summarise(mean_data_score = mean(total_data_score, na.rm = TRUE),
            SD = sd(total_data_score, na.rm = TRUE),
            N = n(),
            stderr = SD/sqrt(N))

data_timeperiod_descriptives

# let's plot this

d2 <- data_timeperiod_descriptives %>%
  ggplot(aes(x = time_period, y = mean_data_score, fill = time_period)) +
  geom_col() +
  geom_errorbar(aes(ymin = mean_data_score - stderr, ymax = mean_data_score + stderr), # specifying what the standard error is
                size=.3, # thinner lines
                width=.2) + # narrower bars
    theme_classic() +
    scale_fill_manual(values=c("#FFCCCC","#FF9999", "#FF6666")) +
  scale_y_continuous(limits = c(0,25), expand = c(0,0)) + # getting the bars to start at the bottom of the graph
  easy_remove_legend() +
  easy_all_text_size(size = 8) + # change the size of the text
  easy_labs(x = "Time Period", y = "Mean Open Data Score") + # change the x and y labels
  ggtitle('(b)')

```

### Interaction between time and subfield - Data scores 

```{r echo=FALSE}
data_subfieldtime_descriptives <- final1A %>%
  group_by(subfield_groups, time_period) %>%
  summarise(mean_data_score = mean(total_data_score, na.rm = TRUE),
            SD = sd(total_data_score, na.rm = TRUE),
            N = n(),
            stderr = SD/sqrt(N))

data_subfieldtime_descriptives

d3 <- data_subfieldtime_descriptives  %>%
  ggplot(aes(x = subfield_groups, y = mean_data_score, fill = time_period)) +
  geom_col(position = "dodge") +
  geom_errorbar(aes(ymin = mean_data_score - stderr, ymax = mean_data_score + stderr), # specifying what the standard error is
                size=.3, # thinner lines
                width=.2, # narrower bars
                position=position_dodge(.9))  +
    theme_classic() +
    scale_fill_manual(values=c("#FFCCCC","#FF9999", "#FF6666")) +
  scale_y_continuous(limits = c(0,25), expand = c(0,0)) + # getting the bars to start at the bottom of the graph
  easy_all_text_size(size = 9) + # change the size of the text
  easy_labs(x = "Subfield", y = "Mean Open Data Score") + # change the x and y labels
  theme(legend.title = element_blank()) + # remove legend title
  ggtitle('(c)')

(d1 | d2) / d3

```

## MATERIALS

### Subfield x Materials Score

```{r echo=FALSE}
materials_subfield_descriptives <- final1A %>%
  group_by(subfield_groups) %>%
  summarise(mean_materials_score = mean(total_materials_score, na.rm = TRUE),
            SD = sd(total_data_score, na.rm = TRUE),
            N = n(),
            stderr = SD/sqrt(N))

materials_subfield_descriptives

# let's plot this

m1 <- materials_subfield_descriptives %>%
  ggplot(aes(x = subfield_groups, y = mean_materials_score, fill = subfield_groups)) +
  geom_col() +
  geom_errorbar(aes(ymin = mean_materials_score - stderr, ymax = mean_materials_score + stderr), # specifying what the standard error is
                size=.3, # thinner lines
                width=.2) + # narrower bars
    theme_classic() +
    scale_fill_manual(values=c("#EC407A","#42A5F5", "#FFCC33", "#00CC99")) +
  scale_y_continuous(limits = c(0,19), expand = c(0,0)) + # getting the bars to start at the bottom of the graph
  easy_remove_legend() +
  easy_all_text_size(size = 8) + # change the size of the text
  easy_labs(x = "Subfield", y = "Mean Open Materials Score") + # change the x and y labels
  ggtitle('(a)')

```

### Time Period x Materials Score

```{r echo=FALSE}
materials_timeperiod_descriptives <- final1A %>%
  group_by(time_period) %>%
  summarise(mean_materials_score = mean(total_materials_score, na.rm = TRUE),
            SD = sd(total_materials_score, na.rm = TRUE),
            N = n(),
            stderr = SD/sqrt(N))

materials_timeperiod_descriptives

# let's plot this

m2 <- materials_timeperiod_descriptives %>%
  ggplot(aes(x = time_period, y = mean_materials_score, fill = time_period)) +
  geom_col() +
  geom_errorbar(aes(ymin = mean_materials_score - stderr, ymax = mean_materials_score + stderr), # specifying what the standard error is
                size=.3, # thinner lines
                width=.2) + # narrower bars
    theme_classic() +
    scale_fill_manual(values=c("#FFCCCC","#FF9999", "#FF6666")) +
  scale_y_continuous(limits = c(0,19), expand = c(0,0)) + # getting the bars to start at the bottom of the graph
  easy_remove_legend() +
  easy_all_text_size(size = 8) + # change the size of the text
  easy_labs(x = "Time Period", y = "Mean Open Materials Score") + # change the x and y labels
  ggtitle('(b)')

```

### Interaction between time and subfield - Materials Score

```{r echo=FALSE}
materials_subfieldtime_descriptives <- final1A %>%
  group_by(subfield_groups, time_period) %>%
  summarise(mean_materials_score = mean(total_materials_score, na.rm = TRUE),
            SD = sd(total_materials_score, na.rm = TRUE),
            N = n(),
            stderr = SD/sqrt(N))

materials_subfieldtime_descriptives 

m3 <- materials_subfieldtime_descriptives  %>%
  ggplot(aes(x = subfield_groups, y = mean_materials_score, fill = time_period)) +
  geom_col(position = "dodge") +
  geom_errorbar(aes(ymin = mean_materials_score - stderr, ymax = mean_materials_score + stderr), # specifying what the standard error is
                size=.3, # thinner lines
                width=.2, # narrower bars
                position=position_dodge(.9)) + 
    theme_classic() +
    scale_fill_manual(values=c("#FFCCCC","#FF9999", "#FF6666")) +
  scale_y_continuous(limits = c(0,19), expand = c(0,0)) + # getting the bars to start at the bottom of the graph
  easy_all_text_size(size = 9) + # change the size of the text
  easy_labs(x = "Subfield", y = "Mean Open Materials Score") + # change the x and y labels
  theme(legend.title = element_blank()) + # remove legend title
  ggtitle('(c)')

(m1 | m2) / m3

```
# SUBFIELD T-TESTS

## DATA 

Subfield main effect for Open Data Scores was not significant, so no t-tests to run here

## MATERIALS

### Developmental vs. Cognition

An independent samples t-test showed that articles published in the the field of Cognition generated significantly higher Open Materials Scores, on average, than articles published in the field of Developmental Psychology,
```{r echo=FALSE}
devcog_materials <- final1A %>%
  filter(subfield_groups %in% c("Development", "Cognition")) 

ttest1 <- t_test(total_materials_score ~ subfield_groups, devcog_materials, paired = FALSE)

t_apa(t_test(total_materials_score ~ subfield_groups, devcog_materials, paired = FALSE))

report(ttest1)
```

### Developmental vs. Social

An independent samples t-test showed that articles published in the the field of Social Psychology generated significantly higher Open Materials Scores, on average, than articles published in the field of Developmental Psychology,
```{r echo=FALSE}
devsocial_materials <- final1A %>%
  filter(subfield_groups %in% c("Development", "Social"))

ttest2 <- t_test(total_materials_score ~ subfield_groups, devsocial_materials, paired = FALSE)

t_apa(t_test(total_materials_score ~ subfield_groups, devsocial_materials, paired = FALSE))

report(ttest2)
```

### Developmental vs. Other

An independent samples t-test showed that articles published in the the Other subfield did not generate significantly higher Open Materials Scores, on average, than articles published in the field of Developmental Psychology,
```{r echo=FALSE}
devother_materials <- final1A %>%
  filter(subfield_groups %in% c("Development", "Other"))

ttest3 <- t_test(total_materials_score ~ subfield_groups, devother_materials, paired = FALSE)

t_apa(t_test(total_materials_score ~ subfield_groups, devother_materials, paired = FALSE))

report(ttest3)
```

# TIME T-TESTS

## DATA

### First half 2014 vs. Second half 2014

An independent samples t-test showed that articles published in the second half of 2014 generated significantly higher Open Data Scores, on average, than articles published in the first half of 2014,
```{r echo=FALSE}
first2014_second2014 <- final1A %>%
  filter(time_period %in% c("1st half 2014", "2nd half 2014"))

ttest4 <- t_test(total_data_score ~ time_period, first2014_second2014, paired = FALSE)

t_apa(t_test(total_data_score ~ time_period, first2014_second2014, paired = FALSE))

report(ttest4) 
```


### Second half 2014 vs. First half 2015

An independent samples t-test showed that articles published in the first half of 2015 did not generate significantly higher Open Data Scores, on average, than articles published in the second half of 2014,
```{r echo=FALSE}
second2014_first2015 <- final1A %>%
  filter(time_period %in% c("2nd half 2014", "1st half 2015"))

ttest5 <- t_test(total_data_score ~ time_period, second2014_first2015, paired = FALSE)

t_apa(t_test(total_data_score ~ time_period, second2014_first2015, paired = FALSE))

report(ttest5)
```

## MATERIALS

### First half 2014 vs. Second half 2014

An independent samples t-test showed that articles published in the second half of 2014 did not generate statistically different Open Data Scores, on average, than articles published in the first half of 2014,
```{r echo=FALSE}
ttest6 <- t_test(total_materials_score ~ time_period, first2014_second2014, paired = FALSE)

t_apa(t_test(total_materials_score ~ time_period, first2014_second2014, paired = FALSE))

report(ttest6)
```

### Second half 2014 vs. First half 2015

An independent samples t-test showed that articles published in the first half of 2015 did not generate statistically different Open Data Scores, on average, than articles published in the second half of 2014,
```{r echo=FALSE}
ttest7 <- t_test(total_materials_score ~ time_period, second2014_first2015, paired = FALSE)

t_apa(t_test(total_materials_score ~ time_period, second2014_first2015, paired = FALSE))

report(ttest7)
```

### First half 2014 vs. First half 2015

An independent samples t-test showed that articles published in the first half of 2015 generated significantly higher Open Data Scores, on average, than articles published in the first half of 2014,
```{r echo=FALSE}
first2014_first2015 <- final1A %>%
  filter(time_period %in% c("1st half 2014", "1st half 2015"))

ttest8 <- t_test(total_materials_score ~ time_period, first2014_first2015, paired = FALSE)

t_apa(t_test(total_materials_score ~ time_period, first2014_first2015, paired = FALSE))

report(ttest8)
```

