---
title: "Confirmatory 1A Analysis Markdown"
output:
  word_document: default
  html_document: default
---
# PREPARATION

## Load Packages
```{r message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(janitor)
library(grid)
library(cowplot)
library(httr)
library(extrafont)
library(here)
library(ggeasy)
library(rstatix)
library(apa)
library(ez)
library(afex)
library(papaja)
library(patchwork)
library(jmv)
```

## Read in data
```{r message=FALSE, warning=FALSE, include=FALSE}
options(scipen=999) # remove scientific notation

data1A <- read_csv(here("data_files", "scored_master_dataset_1A.csv"))
```

## First factor: Subfield
```{r include=FALSE}
# first, let's collapse the subfields into 4 main groups: developmental, cognition, social and 'other'
subfield_groups <- data1A %>%
  mutate(subfield_groups = case_when(subfield == "Behavioural Neuroscience" ~ "Other",
                                     subfield == "Cognitive Neuroscience" ~ "Other",
                                     subfield == "Health Psychology" ~ "Other",
                                     subfield == "Perception" ~ "Other",
                                     subfield == "Developmental Psychology" ~ "Development",
                                     subfield == "Social Psychology" ~  "Social",
                                     TRUE ~ as.character(subfield))) %>%
  relocate(subfield_groups, .after = subfield)

# we can now delete the original subfield column
subfield_groups <- subfield_groups %>%
  select(-subfield)
```

## Second factor: Time 

```{r include=FALSE}
# we want to group the data in 3 six months: first half of 2014, second half of 2014 and first half of 2015

dates <- subfield_groups %>%
  mutate(time_period = case_when(
    str_detect(article_id_number, "1-2014|2-2014|3-2014|4-2014|5-2014|6-2014") ~ "1st half 2014",
    str_detect(article_id_number, "7-2014|8-2014|9-2014|10-2014|11-2014|12-2014") ~ "2nd half 2014",
    str_detect(article_id_number, "1-2015|2-2015|3-2015|4-2015|5-2015") ~ "1st half 2015")) %>%
  relocate(time_period, .after = article_id_number)

```

## Select relevant data 

```{r message=FALSE, include=FALSE}
final1A <- dates %>%
  select(article_id_number, subfield_groups, time_period, total_data_score, total_materials_score)

# make sure subfield and timeperiod are factors 

final1A$subfield_groups <- as.factor(final1A$subfield_groups)
final1A$time_period <- fct_relevel(final1A$time_period, c("1st half 2014", "2nd half 2014", "1st half 2015"))

# check data types

glimpse(final1A)
```

# DATA ANOVA Analysis 

```{r echo=FALSE}
# We decided to use Type II ANOVA tests because this appears to be the more conservative test out of Type I, II and III tests, and is most appropriate for our findings

data_ANOVA <- final1A %>%
  anova_test(total_data_score ~ subfield_groups * time_period)

data_ANOVA

```

Our two-way between-subjects ANOVA generated a significant main effect of time period, F(`r data_ANOVA$DFn[2]`, `r data_ANOVA$DFd[2]`) = `r data_ANOVA$F[1]`, p = `r data_ANOVA$p[2]`, ges = `r data_ANOVA$ges[2]`. However, the main effect of subfield, F(`r data_ANOVA$DFn[1]`, `r data_ANOVA$DFd[1]`) = `r data_ANOVA$F[1]`, p = `r data_ANOVA$p[1]`, ges = `r data_ANOVA$ges[1]`, and the interaction between subfield and time period, F(`r data_ANOVA$DFn[3]`, `r data_ANOVA$DFd[3]`) = `r data_ANOVA$F[3]`, ges = `r data_ANOVA$ges[3]`, were not statistically significant.

  
```{r echo=FALSE}
# Alternatively we can use the papaja package to print the stats: 

data_aov <- aov_ez(
  data = final1A, dv = "total_data_score", 
  id = "article_id_number", 
  between = c("time_period", "subfield_groups"), 
  type = "2")

data_aov$anova_table

data_apa <- apa_print(data_aov)

apa_table(data_apa$table,
          caption = "Between-subjects ANOVA for Open Data Scores", 
          note = "This table was created with apa_table().")
```

Our two-way between-subjects ANOVA generated a significant main effect of time period, `r data_apa$full$time_period`. However, the main effect of subfield, `r data_apa$full$subfield_groups`, and the interaction between time period and subfield, `r data_apa$full$time_period_subfield_groups`, were not statistically significant. 

# MATERIALS ANOVA Analysis 

```{r echo=FALSE}
materials_ANOVA <- final1A %>%
  anova_test(total_materials_score ~ subfield_groups * time_period)

materials_ANOVA
```

Our two-way between-subjects ANOVA generated a significant main effect of subfield, F(`r materials_ANOVA$DFn[1]`, `r materials_ANOVA$DFd[1]`) = `r materials_ANOVA$F[1]`, p = `r materials_ANOVA$p[1]`, ges = `r materials_ANOVA$ges[1]`, and a significant main effect of time period, F(`r materials_ANOVA$DFn[2]`, `r materials_ANOVA$DFd[2]`) = `r materials_ANOVA$F[2]`, p = `r materials_ANOVA$p[2]`, ges = `r materials_ANOVA$ges[2]`. However, the interaction between subfield and time period, F(`r materials_ANOVA$DFn[3]`, `r materials_ANOVA$DFd[3]`) = `r materials_ANOVA$F[3]`, ges = `r materials_ANOVA$ges[3]`, was not statistically significant.

  
```{r echo=FALSE}
# Alternatively we can use the papaja package to print the stats: 

materials_aov <- aov_ez(
  data = final1A, dv = "total_materials_score", 
  id = "article_id_number", 
  between = c("time_period", "subfield_groups"), 
  type = "2")

materials_aov$anova_table

materials_apa <- apa_print(materials_aov)

apa_table(materials_apa$table,
          caption = "Between-subjects ANOVA for Open Materials Scores", 
          note = "This table was created with apa_table().")
```

Our two-way between-subjects ANOVA generated a significant main effect of subfield, `r materials_apa$full$subfield_groups`, and a significant main effect of time period, `r materials_apa$full$time_period`. However the interaction between time period and subfield, `r materials_apa$full$time_period_subfield_groups`, was not statistically significant. 

# PLOTS

## DATA

### Subfield x Data Score

```{r include=FALSE}
data_subfield_descriptives <- final1A %>%
  group_by(subfield_groups) %>%
  summarise(mean_data_score = mean(total_data_score, na.rm = TRUE),
            SD = sd(total_data_score, na.rm = TRUE),
            N = n(),
            stderr = SD/sqrt(N))

# let's plot this

p1 <- data_subfield_descriptives %>%
  ggplot(aes(x = reorder(subfield_groups, mean_data_score), y = mean_data_score, fill = subfield_groups)) +
  geom_col() +
  geom_errorbar(aes(ymin = mean_data_score - stderr, ymax = mean_data_score + stderr), # specifying what the standard error is
                size=.3, # thinner lines
                width=.2) + # narrower bars
  theme_classic() + # white background
  scale_y_continuous(limits = c(0,25), expand = c(0,0)) + # getting the bars to start at the bottom of the graph
  easy_remove_legend() +
  easy_all_text_size(size = 9) + # change the size of the text
  easy_labs(x = "Subfield", y = "Mean Open Data Score") # change the x and y labels
```

### Time Period x Data Score

```{r include=FALSE}
data_timeperiod_descriptives <- final1A %>%
  group_by(time_period) %>%
  summarise(mean_data_score = mean(total_data_score, na.rm = TRUE),
            SD = sd(total_data_score, na.rm = TRUE),
            N = n(),
            stderr = SD/sqrt(N))

# let's plot this

p2 <- data_timeperiod_descriptives %>%
  ggplot(aes(x = time_period, y = mean_data_score, fill = time_period)) +
  geom_col() +
  geom_errorbar(aes(ymin = mean_data_score - stderr, ymax = mean_data_score + stderr), # specifying what the standard error is
                size=.3, # thinner lines
                width=.2) + # narrower bars
  theme_classic() + # white background
  scale_y_continuous(limits = c(0,25), expand = c(0,0)) + # getting the bars to start at the bottom of the graph
  easy_remove_legend() +
  easy_all_text_size(size = 9) + # change the size of the text
  easy_labs(x = "Time Period", y = "Mean Open Data Score")  # change the x and y labels
```

### Interaction between time and subfield - Data scores 

```{r echo=FALSE}
data_subfieldtime_descriptives <- final1A %>%
  group_by(subfield_groups, time_period) %>%
  summarise(mean_data_score = mean(total_data_score, na.rm = TRUE),
            SD = sd(total_data_score, na.rm = TRUE),
            N = n(),
            stderr = SD/sqrt(N))

p3 <- data_subfieldtime_descriptives  %>%
  ggplot(aes(x = subfield_groups, y = mean_data_score, fill = time_period)) +
  geom_col(position = "dodge") +
  geom_errorbar(aes(ymin = mean_data_score - stderr, ymax = mean_data_score + stderr), # specifying what the standard error is
                size=.3, # thinner lines
                width=.2, # narrower bars
                position=position_dodge(.9)) + 
  theme_classic() + # white background
  scale_y_continuous(limits = c(0,25), expand = c(0,0)) + # getting the bars to start at the bottom of the graph
  easy_all_text_size(size = 9) + # change the size of the text
  easy_labs(x = "Subfield", y = "Mean Open Data Score") + # change the x and y labels
  theme(legend.title = element_blank())  # remove legend title

(p1 | p2) / p3
```

## MATERIALS

### Subfield x Materials Score

```{r include=FALSE}
materials_subfield_descriptives <- final1A %>%
  group_by(subfield_groups) %>%
  summarise(mean_materials_score = mean(total_materials_score, na.rm = TRUE),
            SD = sd(total_data_score, na.rm = TRUE),
            N = n(),
            stderr = SD/sqrt(N))

# let's plot this

m1 <- materials_subfield_descriptives %>%
  ggplot(aes(x = reorder(subfield_groups, mean_materials_score), y = mean_materials_score, fill = subfield_groups)) +
  geom_col() +
  geom_errorbar(aes(ymin = mean_materials_score - stderr, ymax = mean_materials_score + stderr), # specifying what the standard error is
                size=.3, # thinner lines
                width=.2) + # narrower bars
  theme_classic() + # white background
  scale_y_continuous(limits = c(0,19), expand = c(0,0)) + # getting the bars to start at the bottom of the graph
  easy_remove_legend() +
  easy_all_text_size(size = 9) + # change the size of the text
  easy_labs(x = "Subfield", y = "Mean Open Materials Score") # change the x and y labels
```

### Time Period x Materials Score

```{r include=FALSE}
materials_timeperiod_descriptives <- final1A %>%
  group_by(time_period) %>%
  summarise(mean_materials_score = mean(total_materials_score, na.rm = TRUE),
            SD = sd(total_materials_score, na.rm = TRUE),
            N = n(),
            stderr = SD/sqrt(N))

# let's plot this

m2 <- materials_timeperiod_descriptives %>%
  ggplot(aes(x = time_period, y = mean_materials_score, fill = time_period)) +
  geom_col() +
  geom_errorbar(aes(ymin = mean_materials_score - stderr, ymax = mean_materials_score + stderr), # specifying what the standard error is
                size=.3, # thinner lines
                width=.2) + # narrower bars
  theme_classic() + # white background
  scale_y_continuous(limits = c(0,19), expand = c(0,0)) + # getting the bars to start at the bottom of the graph
  easy_remove_legend() +
  easy_all_text_size(size = 9) + # change the size of the text
  easy_labs(x = "Time Period", y = "Mean Open Materials Score") # change the x and y labels
```

### Interaction between time and subfield - Materials Score

```{r echo=FALSE}
materials_subfieldtime_descriptives <- final1A %>%
  group_by(subfield_groups, time_period) %>%
  summarise(mean_materials_score = mean(total_materials_score, na.rm = TRUE),
            SD = sd(total_materials_score, na.rm = TRUE),
            N = n(),
            stderr = SD/sqrt(N))

m3 <- materials_subfieldtime_descriptives  %>%
  ggplot(aes(x = subfield_groups, y = mean_materials_score, fill = time_period)) +
  geom_col(position = "dodge") +
  geom_errorbar(aes(ymin = mean_materials_score - stderr, ymax = mean_materials_score + stderr), # specifying what the standard error is
                size=.3, # thinner lines
                width=.2, # narrower bars
                position=position_dodge(.9)) + 
  theme_classic() + # white background
  scale_y_continuous(limits = c(0,19), expand = c(0,0)) + # getting the bars to start at the bottom of the graph
  easy_all_text_size(size = 9) + # change the size of the text
  easy_labs(x = "Subfield", y = "Mean Open Materials Score") # change the x and y labels

(m1 | m2) / m3

```
# SUBFIELD T-TESTS

## DATA 

Subfield main effect for Open Data Scores was not significant, so no t-tests to run here

## MATERIALS

### Developmental vs. Cognition

```{r echo=FALSE}
devcog_materials <- final1A %>%
  filter(subfield_groups %in% c("Development", "Cognition")) %>%
  select(subfield_groups, total_data_score, total_materials_score)

devcog_materials_output <- ttestIS(formula = total_materials_score ~ subfield_groups, data = devcog_materials)

as.data.frame(devcog_materials_output$ttest)
```
https://www.jamovi.org/jmv/ttestis.html 


### Developmental vs. Social

```{r echo=FALSE}
devsocial_materials <- final1A %>%
  filter(subfield_groups %in% c("Development", "Social"))

devsocial_materials_output <- ttestIS(formula = total_materials_score ~ subfield_groups, data = devsocial_materials)

as.data.frame(devsocial_materials_output$ttest)
```

### Developmental vs. Other

```{r echo=FALSE}
devother_materials <- final1A %>%
  filter(subfield_groups %in% c("Development", "Other"))

devother_materials_output <- ttestIS(formula = total_materials_score ~ subfield_groups, data = devother_materials)

as.data.frame(devother_materials_output$ttest)
```

# TIME T-TESTS

## DATA

### First half 2014 vs. Second half 2014

```{r echo=FALSE}
first2014_second2014 <- final1A %>%
  filter(time_period %in% c("1st half 2014", "2nd half 2014")) %>%
  select(time_period, total_data_score, total_materials_score)

glimpse(first2014_second2014)

first2014_second2014_data_output <- ttestIS(formula = total_data_score ~ time_period, data = first2014_second2014)

as.data.frame(first2014_second2014_data_output$ttest)
```


### Second half 2014 vs. First half 2015

```{r echo=FALSE}
second2014_first2015 <- final1A %>%
  filter(time_period %in% c("2nd half 2014", "1st half 2015"))

second2014_first2015_data_output <- ttestIS(formula = total_data_score ~ time_period, data = second2014_first2015)

as.data.frame(second2014_first2015_data_output$ttest)
```

## MATERIALS

### First half 2014 vs. Second half 2014

```{r echo=FALSE}
first2014_second2014_materials_output <- ttestIS(formula = total_materials_score ~ time_period, data = first2014_second2014)

as.data.frame(first2014_second2014_materials_output$ttest)
```

### Second half 2014 vs. First half 2015

```{r echo=FALSE}
second2014_first2015_materials_output <- ttestIS(formula = total_materials_score ~ time_period, data = second2014_first2015)

as.data.frame(second2014_first2015_materials_output$ttest)
```
