---
title: "Exploratory 1B Analysis"
output: html_document
---

Load packages 
```{r message=FALSE, warning=FALSE, include=FALSE}

library(tidyverse)
library(extrafont)
library(here)
library(janitor)
```

Read and clean packages

```{r message=FALSE, warning=FALSE, include=FALSE}

data1B <- read_csv(here("data_files", "scored_master_dataset_1B.csv"))

# first, let's collapse the subfields into 4 main groups: developmental, cognition, social and 'other'
subfield_groups <- data1B %>%
  mutate(subfield_groups = case_when(subfield == "Behavioural Neuroscience" ~ "Other",
                                     subfield == "Cognitive Neuroscience" ~ "Other",
                                     subfield == "Health Psychology" ~ "Other",
                                     subfield == "Perception" ~ "Other",
                                     subfield == "Developmental Psychology" ~ "Development",
                                     subfield == "Social Psychology" ~  "Social",
                                     TRUE ~ as.character(subfield))) %>%
  relocate(subfield_groups, .after = subfield)

# we can now delete the original subfield column
subfield_groups <- subfield_groups %>%
  select(-subfield)
```


# DATA

Select only variables we're interested in

```{r message=FALSE, warning=FALSE, include=FALSE}
select_data <- subfield_groups  %>%
  select(article_id_number, subfield_groups, data_statement_indicates, data_locatable, data_correspond, software, data_codebook, data_scripts, data_complete)

```

Let's create some summary tables

```{r message=FALSE, warning=FALSE, include=FALSE}
# reportedly available
reportedly_available_data <- select_data %>%
  filter(data_statement_indicates == "Available") %>%
  tabyl(subfield_groups, data_statement_indicates) %>%
  mutate("Percent" = Available/(Available)*100) %>%
  select(subfield_groups, Number = Available, Percent) %>%
  mutate(Real_Stage = "Reportedly Available")

# locatable data
locatable_data <- select_data %>%
  filter(data_statement_indicates == "Available") %>%
  tabyl(subfield_groups, data_locatable) %>%
  mutate("Percent" = Yes/(Yes + No + `Requires permission`)*100) %>%
  select(subfield_groups, Number = Yes, Percent) %>%
  mutate(Real_Stage = "Actually Locatable")

# correct data 
correct_data <- select_data %>%
  filter(data_statement_indicates == "Available") %>%
  tabyl(subfield_groups, data_correspond) %>%
  mutate("Percent" = Yes/(Yes + Unclear)*100) %>%
  select(subfield_groups, Number = Yes, Percent) %>%
  mutate(Real_Stage = "Correct Data")

# complete data
complete_data <- select_data %>%
  filter(data_statement_indicates == "Available") %>%
  tabyl(subfield_groups, data_complete) %>%
  mutate("Percent" = `Yes, all of the data appear to be available`/(`Yes, all of the data appear to be available` + `Yes, but only some of the data are available` + `Unclear whether or not all the data are available`)*100) %>%
  select(subfield_groups, Number = `Yes, all of the data appear to be available`, Percent) %>%
  mutate(Real_Stage = "Complete Data")

# software specified
software_specified <- select_data %>%
  filter(data_statement_indicates == "Available") %>%
  tabyl(subfield_groups, software) %>%
  mutate("Percent" = Yes/(Yes + No)*100) %>%
  select(subfield_groups, Number = Yes, Percent) %>%
  mutate(Real_Stage = "Software Specified")

# codebook available 
data_codebook_available <- select_data %>%
  filter(data_statement_indicates == "Available") %>%
  tabyl(subfield_groups, data_codebook) %>%
  mutate("Percent" = Yes/(Yes + No)*100) %>%
  select(subfield_groups, Number = Yes, Percent) %>%
  mutate(Real_Stage = "Codebook Available")

# scripts available 
data_scripts_available <- select_data %>%
  filter(data_statement_indicates == "Available") %>%
  tabyl(subfield_groups, data_scripts) %>%
  mutate("Percent" = Yes/(Yes + No)*100) %>%
  select(subfield_groups, Number = Yes, Percent) %>%
  mutate(Real_Stage = "Scripts Available")
```

Let's bind all these statistics together

```{r message=FALSE, warning=FALSE, include=FALSE}
all_data_stats <- rbind(reportedly_available_data, locatable_data, correct_data, complete_data, software_specified, data_codebook_available, data_scripts_available)%>%
  relocate(subfield_groups, .after = `Real_Stage`) %>%
  relocate(Number, .after = subfield_groups) %>%
  relocate(Percent, .after = Number)

```

Let's plot

```{r echo=FALSE}
data_plot <- ggplot(all_data_stats, aes(y=Percent,  group = subfield_groups, colour = subfield_groups)) +
  coord_cartesian(ylim=c(0,100)) +
  geom_line(aes(colour=subfield_groups, x=Real_Stage)) +
  geom_point(aes(x=Real_Stage), size=3, position = position_dodge(width=0)) +
  scale_color_manual(values=c("#FF6666","#6699CC", "#FFCC33", "#00CC99"),
                     labels=c("Development",
                              "Social",
                              "Cognition",
                              "Other")) +
  scale_size_manual(name= "subfield_groups",
                    values=c(2,
                             2,
                             2,
                             2),
                    guide=F) +
  theme(axis.text.y = element_text(size=9),
        axis.title.y = element_text(size=9)) +
  theme(axis.text.x = element_text(size=7)) +
  scale_x_discrete(limits=c("Reportedly Available","Actually Locatable","Correct Data","Complete Data", "Codebook Available", "Software Specified", "Scripts Available"))+
  ylab("Percentage of Articles with Data Reportedly Available") +
  theme(legend.position=c(.125, .3)) +
  theme(legend.title=element_blank()) +
  theme(legend.text = element_text(size = 8)) +
  theme(legend.key.size = unit(1, "cm")) +
  guides(colour = guide_legend(override.aes = list(size = 1, shape = NA))) +
  theme(axis.line= element_line(), axis.title.x=element_blank(), 
        panel.background = element_blank(), 
        panel.grid.minor = element_blank()) 

data_plot

```
Now let's generate a table that summarises the number of articles in each category as opposed to the percentage

```{r eval=FALSE, include=FALSE}

data_percentages <- all_data_stats %>%
  pivot_wider(names_from = subfield_groups, values_from = "Number", c("Real_Stage", "Number")) %>%
  select(" " = Real_Stage, Development, Social, Cognition, Other)

data_summary <- gt(data_percentages) %>%
  tab_style(style = list(
  cell_text(color = "black", font = "Times New Roman", size = 16, align = "center")),
  locations = cells_body()) %>%
    tab_style(style = list(
  cell_text(color = "black", font = "Times New Roman", size = 16, align = "center")),
  locations = cells_column_labels()) %>%
  tab_style(style = list(
    cell_borders(
    sides = c("top", "bottom"), 
    color = NULL)), # setting the colour to NULL removes the borders entirely 
      locations = cells_body()) %>%
  tab_options(
    table_body.border.bottom.color = "black", # bottom-most border
    column_labels.border.top.color = "black",
    column_labels.border.bottom.color = "black", 
    table.width = pct(30)) 

data_summary

# I've done a bit of research and it looks like there is an issue with the current gt() package in that you can't change the weight of the borders

# In case the issue is resolved, this is the code you would add to the above script to change the weight of the borders
  #tab_options(
    #table_body.border.bottom.width = 1, # bottom-most border
    #column_labels.border.top.width = 1,
    #column_labels.border.bottom.width = 1)


# Let's save the gt as a pdf (This is the nicest format to screenshot into a word doc)

data_summary %>%
  gtsave("Table 4.pdf")


```

# MATERIALS

Select only the variables we're interested in

```{r message=FALSE, warning=FALSE, include=FALSE}
select_materials <- subfield_groups %>%
  select(article_id_number, subfield_groups, materials_statement_indicates, materials_locatable, materials_correspond, materials_complete, materials_explanation)
```

Let's create some summary tables

```{r message=FALSE, warning=FALSE, include=FALSE}
# reportedly available
reportedly_available_materials <- select_materials %>%
  filter(materials_statement_indicates == "Available") %>%
  tabyl(subfield_groups, materials_statement_indicates) %>%
  mutate("Percent" = Available/(Available)*100) %>%
  select(subfield_groups, Number = Available, Percent) %>%
  mutate(Real_Stage = "Reportedly Available")

# locatable materials
locatable_materials <- select_materials %>%
  filter(materials_statement_indicates == "Available") %>%
  tabyl(subfield_groups, materials_locatable) %>%
  mutate("Percent" = Yes/(Yes + No + `Requires permission`)*100) %>%
  select(subfield_groups, Number = Yes, Percent) %>%
  mutate(Real_Stage = "Actually Locatable")

# correct materials
correct_materials <- select_materials %>%
  filter(materials_statement_indicates == "Available") %>%
  tabyl(subfield_groups, materials_correspond) %>%
  mutate("Percent" = Yes/(Yes + Unclear)*100) %>%
  select(subfield_groups, Number = Yes, Percent) %>%
  mutate(Real_Stage = "Correct Materials")

# complete materials
complete_materials <- select_materials %>%
  filter(materials_statement_indicates == "Available") %>%
  tabyl(subfield_groups, materials_complete) %>%
  mutate("Percent" = `Yes, all of the materials appear to be available`/(`Yes, all of the materials appear to be available` + `Yes, but only some of the materials are available` + `No, not all of the materials are available` + `Unclear whether or not all the materials are available`)*100) %>%
  select(subfield_groups, Number = `Yes, all of the materials appear to be available`, Percent) %>%
  mutate(Real_Stage = "Complete Materials")

# scripts available 
material_scripts_available <- select_materials %>%
  filter(materials_statement_indicates == "Available") %>%
  tabyl(subfield_groups, materials_explanation) %>%
  mutate("Percent" = Yes/(Yes + No)*100) %>%
  select(subfield_groups, Number = Yes, Percent) %>%
  mutate(Real_Stage = "Scripts Available")
```

Let's bind all these statistics together

```{r message=FALSE, warning=FALSE, include=FALSE}
all_material_stats <- rbind(reportedly_available_materials, locatable_materials, correct_materials, complete_materials, material_scripts_available)%>%
  relocate(subfield_groups, .after = `Real_Stage`) %>%
  relocate(Number, .after = subfield_groups) %>%
  relocate(Percent, .after = Number)

```

Let's plot

```{r echo=FALSE}

materials_plot <- ggplot(all_material_stats, aes(y=Percent,  group = subfield_groups, colour = subfield_groups)) +
  coord_cartesian(ylim=c(0,100)) +
  geom_line(aes(colour=subfield_groups, x=Real_Stage)) +
  geom_point(aes(x=Real_Stage), size=3, position = position_dodge(width=0)) +
  scale_color_manual(values=c("#FF6666","#6699CC", "#FFCC33", "#00CC99"),
                     labels=c("Development",
                              "Social",
                              "Cognition",
                              "Other")) +
  scale_size_manual(name= "subfield_groups",
                    values=c(2,
                             2,
                             2,
                             2),
                    guide=F) +
  theme(axis.text.y = element_text(size=9),
        axis.title.y = element_text(size=9)) +
  theme(axis.text.x = element_text(size=7)) +
  scale_x_discrete(limits=c("Reportedly Available","Actually Locatable","Correct Materials","Complete Materials", "Scripts Available")) +
  ylab("Percentage of Articles with Materials Reportedly Available") +
  theme(legend.position=c(.125, .3)) +
  theme(legend.title=element_blank()) +
  theme(legend.text = element_text(size = 8)) +
  theme(legend.key.size = unit(1, "cm")) +
  guides(colour = guide_legend(override.aes = list(size = 1, shape = NA))) +
  theme(axis.line= element_line(), axis.title.x=element_blank(), 
        panel.background = element_blank(), 
        panel.grid.minor = element_blank()) 

materials_plot

```


Now let's generate a table that summarises the number of articles in each category as opposed to the percentage

```{r eval=FALSE, include=FALSE}

materials_percentages <- all_material_stats %>%
  pivot_wider(names_from = subfield_groups, values_from = "Number", c("Real_Stage", "Number")) %>%
  select(" " = Real_Stage, Development, Social, Cognition, Other)

materials_summary <- gt(materials_percentages) %>%
  tab_style(style = list(
  cell_text(color = "black", font = "Times New Roman", size = 16, align = "center")),
  locations = cells_body()) %>%
    tab_style(style = list(
  cell_text(color = "black", font = "Times New Roman", size = 16, align = "center")),
  locations = cells_column_labels()) %>%
  tab_style(style = list(
    cell_borders(
    sides = c("top", "bottom"), 
    color = NULL)), # setting the colour to NULL removes the borders entirely 
      locations = cells_body()) %>%
  tab_options(
    table_body.border.bottom.color = "black", # bottom-most border
    column_labels.border.top.color = "black",
    column_labels.border.bottom.color = "black", 
    table.width = pct(30)) 

materials_summary

# Let's save this as a pdf

materials_summary %>%
  gtsave("Table 5.pdf")

```
