---
title: "Reportedly Available x Subfield Analysis"
output: html_document
---
# Load packages 
```{r message=FALSE, warning=FALSE, include=FALSE}

library(tidyverse)
library(extrafont)
library(here)
library(janitor)
library(gt)
library(webshot)
library(apa)
library(patchwork)
```

# DATA

## 1A DATA

Read and clean 1A data 

```{r message=FALSE, warning=FALSE, include=FALSE}

data1A <- read_csv(here("data_files", "scored_master_dataset_1A.csv"))

# first, let's collapse the subfields into 4 main groups: developmental, cognition, social and 'other'
A_subfield_groups <- data1A %>%
  mutate(subfield_groups = case_when(subfield == "Behavioural Neuroscience" ~ "Other",
                                     subfield == "Cognitive Neuroscience" ~ "Other",
                                     subfield == "Health Psychology" ~ "Other",
                                     subfield == "Perception" ~ "Other",
                                     subfield == "Developmental Psychology" ~ "Development",
                                     subfield == "Social Psychology" ~  "Social",
                                     TRUE ~ as.character(subfield))) %>%
  relocate(subfield_groups, .after = subfield)

# we can now delete the original subfield column
A_subfield_groups <- A_subfield_groups %>%
  select(-subfield)
```

Let's calculate the percentage of articles that had reportedly available data

```{r message=FALSE, warning=FALSE, include=FALSE}
A_reportedly_available_data <- A_subfield_groups %>%
    tabyl(subfield_groups, data_statement_indicates_that_data_are) %>%
  mutate("Percent" = Available/(Available + `No statement` + Unavailable)*100) %>%
  select(subfield_groups, Number = Available, Percent) %>%
  mutate(Time = "2014-15")

```

## 1B DATA

Read and clean 1B data

```{r message=FALSE, warning=FALSE, include=FALSE}

data1B <- read_csv(here("data_files", "scored_master_dataset_1B.csv"))

# first, let's collapse the subfields into 4 main groups: developmental, cognition, social and 'other'
B_subfield_groups <- data1B %>%
  mutate(subfield_groups = case_when(subfield == "Behavioural Neuroscience" ~ "Other",
                                     subfield == "Cognitive Neuroscience" ~ "Other",
                                     subfield == "Health Psychology" ~ "Other",
                                     subfield == "Perception" ~ "Other",
                                     subfield == "Developmental Psychology" ~ "Development",
                                     subfield == "Social Psychology" ~  "Social",
                                     TRUE ~ as.character(subfield))) %>%
  relocate(subfield_groups, .after = subfield)

# we can now delete the original subfield column
B_subfield_groups <- B_subfield_groups %>%
  select(-subfield)
```

Let's calculate the percentage of articles that had reportedly available materials

```{r message=FALSE, warning=FALSE, include=FALSE}
B_reportedly_available_data <- B_subfield_groups %>%
    tabyl(subfield_groups, data_statement_indicates) %>%
  mutate("Percent" = Available/(Available + Unavailable + `NA_`)*100) %>%
  select(subfield_groups, Number = Available, Percent) %>%
  mutate(Time = "2019-20")

```

Let's combine the statistics

```{r}
all_data <- rbind(A_reportedly_available_data, B_reportedly_available_data)
```

Let's graph this

```{r}
all_data$subfield_groups <- fct_relevel(all_data$subfield_groups, c("Development", "Social", "Cognition", "Other"))

data <- all_data %>%
  ggplot(aes(x = subfield_groups, y = Percent, fill = Time)) +
  geom_col(position = "dodge") +
  theme_classic() +
  scale_fill_manual(values=c("#FF6666","#6699CC"),
                     labels=c("2014-19",
                              "2019-20")) +
 theme(axis.text.y = element_text(size=9),
        axis.title.y = element_text(size=7)) +
  theme(axis.text.x = element_text(size=9)) +
  easy_labs(y = "Percentage of Articles with Reportedly\nAvailable Data") + 
  easy_remove_x_axis(what = c("title")) +
  theme(legend.title = element_blank()) + # remove legend title
    scale_y_continuous(limits = c(0,100), expand = c(0,0)) 

data
```

# MATERIALS

# 1A MATERIALS

Let's calculate the percentage of articles that had reportedly available materials

```{r message=FALSE, warning=FALSE, include=FALSE}
A_reportedly_available_materials <- A_subfield_groups %>%
    tabyl(subfield_groups, statement_indicates_that_materials_are) %>%
  mutate("Percent" = Available/(Available + `No statement`)*100) %>%
  select(subfield_groups, Number = Available, Percent) %>%
  mutate(Time = "2014-15")

```

# 1B MATERIALS

Let's calculate the percentage of articles that had reportedly available materials

```{r message=FALSE, warning=FALSE, include=FALSE}
B_reportedly_available_materials <- B_subfield_groups %>%
    tabyl(subfield_groups, materials_statement_indicates) %>%
  mutate("Percent" = Available/(Available + Unavailable + `NA_`)*100) %>%
  select(subfield_groups, Number = Available, Percent) %>%
  mutate(Time = "2019-20")

```

Let's combine the statistics

```{r}
all_materials <- rbind(A_reportedly_available_materials, B_reportedly_available_materials)
```

Let's graph this

```{r}
all_materials$subfield_groups <- fct_relevel(all_materials$subfield_groups, c("Development", "Social", "Cognition", "Other"))

materials <- all_materials %>%
  ggplot(aes(x = subfield_groups, y = Percent, fill = Time)) +
  geom_col(position = "dodge") +
  theme_classic() +
  scale_fill_manual(values=c("#FF6666","#6699CC"),
                     labels=c("2014-19",
                              "2019-20")) +
 theme(axis.text.y = element_text(size=9),
        axis.title.y = element_text(size=7)) +
  theme(axis.text.x = element_text(size=9)) +
  easy_labs(y = "Percentage of Articles with Reportedly\nAvailable Materials") + 
  easy_remove_x_axis(what = c("title")) +
  theme(legend.title = element_blank()) + # remove legend title
    scale_y_continuous(limits = c(0,100), expand = c(0,0)) 

materials

data /
  materials + plot_layout(guides='collect') &
theme(legend.position='right')

```