---
title: "Supplementary Figures (2014-15)"
output:
  pdf_document: default
  word_document: default
  html_document: default
---

### The following figure illustrates the proportion of *Psychological Science* articles, published between January 2014 and May 2015, that  met a series of data sharing criteria, of those that reported having openly accessible data. 

### The criteria are as follows:

##### Reportedly Available: Data was reported to be available in the article
##### Actually Locatable: Data was actually located at the reported URL link
##### Correct Data: Data corresponded to what was reported in the article
##### Complete Data: The full set of data were available
##### Codebook Available: A codebook that defined what each variable in the dataset referred to, was available with the data
##### Software Specified: The software that was used to analyse the data, was specified
##### Scripts Available: Analysis scripts or code were available with the data


```{r message=FALSE, warning=FALSE, include=FALSE}
# Load packages 

library(tidyverse)
library(extrafont)
library(here)
library(janitor)
library(ggeasy)

```


```{r message=FALSE, warning=FALSE, include=FALSE}

# Read and clean data 

data1A <- read_csv(here("data_files", "scored_master_dataset_1A.csv"))

# Note: you will need to change the location of the file, depending on where you have saved it

# Assign articles to subfield groups
subfield_groups <- data1A %>%
  mutate(subfield_groups = case_when(subfield == "Behavioural Neuroscience" ~ "Other",
                                     subfield == "Cognitive Neuroscience" ~ "Other",
                                     subfield == "Health Psychology" ~ "Other",
                                     subfield == "Perception" ~ "Other",
                                     subfield == "Developmental Psychology" ~ "Development",
                                     subfield == "Social Psychology" ~  "Social",
                                     TRUE ~ as.character(subfield))) %>%
  relocate(subfield_groups, .after = subfield)

# Delete the original subfield column
subfield_groups <- subfield_groups %>%
  select(-subfield)
```



```{r message=FALSE, warning=FALSE, include=FALSE}
# DATA

# Select only relevant data

select_data <- subfield_groups  %>%
  select(article_id_number, subfield_groups, data_statement_indicates_that_data_are, are_the_data_located_at_the_working_page, does_the_data_correspond_to_what_is_reported_in_the_article, software, is_a_codebook_included_with_the_data_or_other_means_of_understanding_the_variables, are_analysis_scripts_included_with_the_data, are_the_data_complete)

```


```{r message=FALSE, warning=FALSE, include=FALSE}
# Summary tables

# reportedly available
reportedly_available_data <- select_data %>%
  filter(data_statement_indicates_that_data_are == "Available") %>%
  tabyl(subfield_groups, data_statement_indicates_that_data_are) %>%
  mutate("Percent" = Available/(Available)*100) %>%
  select(subfield_groups, Number = Available, Percent) %>%
  mutate(Real_Stage = "Reportedly Available")

# locatable data
locatable_data <- select_data %>%
  filter(data_statement_indicates_that_data_are == "Available") %>%
  tabyl(subfield_groups, are_the_data_located_at_the_working_page) %>%
  mutate("Percent" = Yes/(Yes + No + `Requires permission`)*100) %>%
  select(subfield_groups, Number = Yes, Percent) %>%
  mutate(Real_Stage = "Actually Locatable")

# correct data 
correct_data <- select_data %>%
  filter(data_statement_indicates_that_data_are == "Available") %>%
  tabyl(subfield_groups, does_the_data_correspond_to_what_is_reported_in_the_article) %>%
  mutate("Percent" = Yes/(Yes + Unclear)*100) %>%
  select(subfield_groups, Number = Yes, Percent) %>%
  mutate(Real_Stage = "Correct Data")

# complete data
complete_data <- select_data %>%
  filter(data_statement_indicates_that_data_are == "Available") %>%
  tabyl(subfield_groups, are_the_data_complete) %>%
  mutate("Percent" = `Yes, all of the data appear to be available`/(`Yes, all of the data appear to be available` + `Yes, but only some of the data are available` + `No, not all of the data are available` + `Unclear whether or not all of the data are available`)*100) %>%
  select(subfield_groups, Number = `Yes, all of the data appear to be available`, Percent) %>%
  mutate(Real_Stage = "Complete Data")

# software specified
software_specified <- select_data %>%
  filter(data_statement_indicates_that_data_are == "Available") %>%
  tabyl(subfield_groups, software) %>%
  mutate("Percent" = Yes/(Yes + No)*100) %>%
  select(subfield_groups, Number = Yes, Percent) %>%
  mutate(Real_Stage = "Software Specified")

# codebook available 
data_codebook_available <- select_data %>%
  filter(data_statement_indicates_that_data_are == "Available") %>%
  tabyl(subfield_groups, is_a_codebook_included_with_the_data_or_other_means_of_understanding_the_variables) %>%
  mutate("Percent" = Yes/(Yes + No)*100) %>%
  select(subfield_groups, Number = Yes, Percent) %>%
  mutate(Real_Stage = "Codebook Available")

# scripts available 
data_scripts_available <- select_data %>%
  filter(data_statement_indicates_that_data_are == "Available") %>%
  tabyl(subfield_groups, are_analysis_scripts_included_with_the_data) %>%
  mutate("Percent" = Yes/(Yes + No)*100) %>%
  select(subfield_groups, Number = Yes, Percent) %>%
  mutate(Real_Stage = "Scripts Available")
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
# Bind all statistics together

all_data_stats <- rbind(reportedly_available_data, locatable_data, correct_data, complete_data, software_specified, data_codebook_available, data_scripts_available)%>%
  relocate(subfield_groups, .after = `Real_Stage`) %>%
  relocate(Number, .after = subfield_groups) %>%
  relocate(Percent, .after = Number)

```


```{r echo=FALSE, warning=FALSE}
# Plot

data_plot <- ggplot(all_data_stats, aes(y=Percent, group = subfield_groups, colour = subfield_groups)) +
  coord_cartesian(ylim=c(0,100)) +
  geom_line(aes(colour=subfield_groups, x=Real_Stage)) +
  geom_point(aes(x=Real_Stage), size=3, position = position_dodge(width=0)) +
  scale_color_manual(values=c("#EC407A","#42A5F5", "#FFCC33", "#00CC99"),
                     labels=c("Development (n = 9)",
                              "Social (n = 28) ",
                              "Cognition (n = 24)",
                              "Other (n = 12)")) +
  scale_size_manual(name= "subfield_groups",
                    values=c(2,
                             2,
                             2,
                             2),
                    guide=F) +
  theme(axis.text.y = element_text(size=9),
        axis.title.y = element_text(size=9)) +
  theme(axis.text.x = element_text(size=7),
        axis.title.x = element_text(size=9, margin = margin(t = 8, r = 0, b = 0, l = 0))) +
  easy_labs(y = "Percentage of Articles with Data Reportedly Available", x = "Data Sharing Criteria") +
  scale_x_discrete(limits=c("Reportedly Available","Actually Locatable","Correct Data","Complete Data", "Codebook Available", "Software Specified", "Scripts Available"))+
  theme(legend.position=c(.2, .3)) +
  theme(legend.title=element_blank()) +
  theme(legend.text = element_text(size = 8)) +
  theme(legend.key.size = unit(1, "cm")) +
  guides(colour = guide_legend(override.aes = list(size = 1, shape = NA))) +
  theme(axis.line= element_line(),
        panel.background = element_blank(), 
        panel.grid.minor = element_blank()) 
  

data_plot

```


```{r eval=FALSE, include=FALSE}

# Summary table

# This table illustrates the number of articles (as opposed to the proportion) that met each data sharing criteria.

data_percentages <- all_data_stats %>%
  pivot_wider(names_from = subfield_groups, values_from = "Number", c("Real_Stage", "Number")) %>%
  select(" " = Real_Stage, Development, Social, Cognition, Other)

data_summary <- gt(data_percentages) %>%
  tab_style(style = list(
  cell_text(color = "black", font = "Times New Roman", size = 16, align = "center")),
  locations = cells_body()) %>%
    tab_style(style = list(
  cell_text(color = "black", font = "Times New Roman", size = 16, align = "center")),
  locations = cells_column_labels()) %>%
  tab_style(style = list(
    cell_borders(
    sides = c("top", "bottom"), 
    color = NULL)), # setting the colour to NULL removes the borders entirely 
      locations = cells_body()) %>%
  tab_options(
    table_body.border.bottom.color = "black", # bottom-most border
    column_labels.border.top.color = "black",
    column_labels.border.bottom.color = "black", 
    table.width = pct(30)) 

data_summary


```

### The following figure illustrates the proportion of *Psychological Science* articles, published between January 2014 and May 2015, that met a series of materials sharing criteria, of those that reported having openly accessible materials. 

### The criteria are as follows:

##### Reportedly Available: Materials were reported to be available in the article
##### Actually Locatable: Materials were actually located at the reported URL link
##### Correct Materials: Materials corresponded to what was reported in the article
##### Complete Materials: The full set of materials were available
##### Scripts Available/Explanation Provided: Scripts or code that were used to generate or operate the materials were available, or an explanation of how the materials were used in the study was available

```{r message=FALSE, warning=FALSE, include=FALSE}
# MATERIALS

# Select only relevant data

select_materials <- subfield_groups %>%
  select(article_id_number, subfield_groups, statement_indicates_that_materials_are, are_the_materials_located_at_the_working_page, do_the_materials_correspond_to_what_is_reported_in_the_article, are_the_materials_complete, are_analysis_scripts_included_with_the_materials)
```


```{r message=FALSE, warning=FALSE, include=FALSE}
# Summary tables

# reportedly available
reportedly_available_materials <- select_materials %>%
  filter(statement_indicates_that_materials_are == "Available") %>%
  tabyl(subfield_groups, statement_indicates_that_materials_are) %>%
  mutate("Percent" = Available/(Available)*100) %>%
  select(subfield_groups, Number = Available, Percent) %>%
  mutate(Real_Stage = "Reportedly Available")

# locatable materials
locatable_materials <- select_materials %>%
  filter(statement_indicates_that_materials_are == "Available") %>%
  tabyl(subfield_groups, are_the_materials_located_at_the_working_page) %>%
  mutate("Percent" = Yes/(Yes + No + `Requires permission`)*100) %>%
  select(subfield_groups, Number = Yes, Percent) %>%
  mutate(Real_Stage = "Actually Locatable")

# correct materials
correct_materials <- select_materials %>%
  filter(statement_indicates_that_materials_are == "Available") %>%
  tabyl(subfield_groups, do_the_materials_correspond_to_what_is_reported_in_the_article) %>%
  mutate("Percent" = Yes/(Yes + Unclear)*100) %>%
  select(subfield_groups, Number = Yes, Percent) %>%
  mutate(Real_Stage = "Correct Materials")

# complete materials
complete_materials <- select_materials %>%
  filter(statement_indicates_that_materials_are == "Available") %>%
  tabyl(subfield_groups, are_the_materials_complete) %>%
  mutate("Percent" = `Yes, all of the materials appear to be available`/(`Yes, all of the materials appear to be available` + `Yes, but only some of the materials are available` + `No, not all of the materials are available` + `Unclear whether or not all of the materials are available`)*100) %>%
  select(subfield_groups, Number = `Yes, all of the materials appear to be available`, Percent) %>%
  mutate(Real_Stage = "Complete Materials")

# scripts available 
material_scripts_available <- select_materials %>%
  filter(statement_indicates_that_materials_are == "Available") %>%
  tabyl(subfield_groups, are_analysis_scripts_included_with_the_materials) %>%
  mutate("Percent" = Yes/(Yes + No)*100) %>%
  select(subfield_groups, Number = Yes, Percent) %>%
  mutate(Real_Stage = "Scripts Available")
```


```{r message=FALSE, warning=FALSE, include=FALSE}
# Bind all statistics together

all_material_stats <- rbind(reportedly_available_materials, locatable_materials, correct_materials, complete_materials, material_scripts_available)%>%
  relocate(subfield_groups, .after = `Real_Stage`) %>%
  relocate(Number, .after = subfield_groups) %>%
  relocate(Percent, .after = Number)

```


```{r echo=FALSE, warning=FALSE}
# Plot

materials_plot <- ggplot(all_material_stats, aes(y=Percent,  group = subfield_groups, colour = subfield_groups)) +
  coord_cartesian(ylim=c(0,100)) +
  geom_line(aes(colour=subfield_groups, x=Real_Stage)) +
  geom_point(aes(x=Real_Stage), size=3, position = position_dodge(width=0)) +
  scale_color_manual(values=c("#EC407A","#42A5F5", "#FFCC33", "#00CC99"),
                     labels=c("Development (n = 10)",
                              "Social (n = 33)",
                              "Cognition (n = 36)",
                              "Other (n = 18)")) +
  scale_size_manual(name= "subfield_groups",
                    values=c(2,
                             2,
                             2,
                             2),
                    guide=F) +
  theme(axis.text.y = element_text(size=9),
        axis.title.y = element_text(size=9)) +
  theme(axis.text.x = element_text(size=7),
        axis.title.x = element_text(size=9, margin = margin(t = 8, r = 0, b = 0, l = 0))) +
  easy_labs(y = "Percentage of Articles with Materials Reportedly Available", x = "Material Sharing Criteria") +
  scale_x_discrete(limits=c("Reportedly Available","Actually Locatable","Correct Materials","Complete Materials", "Scripts Available")) +
  theme(legend.position=c(.2, .25)) +
  theme(legend.title=element_blank()) +
  theme(legend.text = element_text(size = 8)) +
  theme(legend.key.size = unit(1, "cm")) +
  guides(colour = guide_legend(override.aes = list(size = 1, shape = NA))) +
  theme(axis.line= element_line(),
        panel.background = element_blank(), 
        panel.grid.minor = element_blank()) 

materials_plot

```


```{r eval=FALSE, include=FALSE}

# Summary table

# This table illustrates the number of articles (as opposed to the proportion) that met each data sharing criteria.

materials_percentages <- all_material_stats %>%
  pivot_wider(names_from = subfield_groups, values_from = "Number", c("Real_Stage", "Number")) %>%
  select(" " = Real_Stage, Development, Social, Cognition, Other)

materials_summary <- gt(materials_percentages) %>%
  tab_style(style = list(
  cell_text(color = "black", font = "Times New Roman", size = 16, align = "center")),
  locations = cells_body()) %>%
    tab_style(style = list(
  cell_text(color = "black", font = "Times New Roman", size = 16, align = "center")),
  locations = cells_column_labels()) %>%
  tab_style(style = list(
    cell_borders(
    sides = c("top", "bottom"), 
    color = NULL)), # setting the colour to NULL removes the borders entirely 
      locations = cells_body()) %>%
  tab_options(
    table_body.border.bottom.color = "black", # bottom-most border
    column_labels.border.top.color = "black",
    column_labels.border.bottom.color = "black", 
    table.width = pct(30)) 

materials_summary


```
