---
title: "Study 1B Confirmatory Analysis (2014-15 vs. 2019-20) Output"
output:
  html_document: default
  word_document: default
---

```{r message=FALSE, warning=FALSE, include=FALSE}
## Load Packages

library(tidyverse)
library(janitor)
library(here)
library(ggeasy)
library(apa)
library(papaja)
library(patchwork)
library(afex)
library(report)
library(ggsignif)
```


```{r message=FALSE, warning=FALSE, include=FALSE}

options(scipen=999) # remove scientific notation

## Read in Study 1A data

data1A <- read_csv(here("Working", "data_files", "Scored Study 1A Master Dataset.csv"))

# Note: you will need to change the location of the file, depending on where you have saved it

## Select only relevant Study 1A data

data1Aselect <- data1A %>%
  select(article_id_number, subfield, open_data_score, open_materials_score)
```

```{r message=FALSE, warning=FALSE, include=FALSE}
## Read in Study 1B data

data1B <- read_csv(here("Working", "data_files", "Scored Study 1B Master Dataset.csv"))

## Select only relevant Study 1B data 

data1Bselect <- data1B %>%
  select(article_id_number, subfield, open_data_score, open_materials_score)
```


```{r include=FALSE}
## Merge 1A and 1B data into one dataframe

alldata <- rbind(data1Aselect, data1Bselect)
```

## First factor: Subfield 

```{r echo=FALSE}
# Assign articles to subfield groups
subfield_groups <- alldata %>%
  mutate(subfield_groups = case_when(subfield == "Behavioural Neuroscience" ~ "Other",
                                     subfield == "Cognitive Neuroscience" ~ "Other",
                                     subfield == "Health Psychology" ~ "Other",
                                     subfield == "Perception" ~ "Other",
                                     subfield == "Developmental Psychology" ~ "Development",
                                     subfield == "Social Psychology" ~  "Social",
                                     TRUE ~ as.character(subfield))) %>%
  relocate(subfield_groups, .after = subfield)

# Delete the original subfield column
subfield_groups <- subfield_groups %>%
  select(-subfield)

# Subfield summary

subfield_summary <- subfield_groups %>%
    count(subfield_groups) 

subfield_summary
```

## Second factor: Time period

```{r echo=FALSE}
dates <- subfield_groups %>%
  mutate(time_period = case_when(
    str_detect(article_id_number, "1-2014|2-2014|3-2014|4-2014|5-2014|6-2014|7-2014|8-2014|9-2014|10-2014|11-2014|12-2014|1-2015|2-2015|3-2015|4-2015|5-2015") ~ "2014-15",
    str_detect(article_id_number, "2019-30-7|2019-30-8|2019-30-9|2019-30-10|2019-30-11|2019-30-12|2020-31-1|2020-31-2|2020-31-3|2020-31-4|2020-31-5|2020-31-6|2020-31-7|2020-31-8|2020-31-9|2020-31-10|2020-31-11|2020-31-12") ~ "2019-20")) %>%
  relocate(time_period, .after = article_id_number)

# Set subfield and timeperiod variables as factors 

dates$subfield_groups <- fct_relevel(dates$subfield_groups, c("Development", "Social", "Cognition", "Other"))
dates$time_period <- fct_relevel(dates$time_period, c("2014-15", "2019-20"))

# Timeperiod summary

timeperiod_summary <- dates %>%
  count(time_period)

timeperiod_summary
```

# DATA ANOVA

```{r echo=FALSE, message=FALSE, warning=FALSE}

data_aov <- aov_ez(
  data = dates, dv = "open_data_score", 
  id = "article_id_number", 
  between = c("time_period", "subfield_groups"), 
  type = "2")

data_apa <- apa_print(data_aov)

apa_table(data_apa$table,
          caption = "Between-subjects ANOVA for Open Data Scores")
```

Our two-way between-subjects ANOVA generated a significant main effect of time period, `r data_apa$full$time_period`, and a significant main effect of subfield, `r data_apa$full$subfield_groups`. However, the interaction between time period and subfield, `r data_apa$full$time_period_subfield_groups`, was not statistically significant. 

# MATERIALS ANOVA Analysis 

```{r echo=FALSE, message=FALSE, warning=FALSE}

materials_aov <- aov_ez(
  data = dates, dv = "open_materials_score", 
  id = "article_id_number", 
  between = c("time_period", "subfield_groups"), 
  type = "2")

materials_apa <- apa_print(materials_aov)

apa_table(materials_apa$table,
          caption = "Between-subjects ANOVA for Open Materials Scores")
```

Our two-way between-subjects ANOVA generated a significant main effect of subfield, `r materials_apa$full$subfield_groups`, and time period, `r materials_apa$full$time_period`. However, the interaction between time period and subfield, `r materials_apa$full$time_period_subfield_groups`, was not statistically significant. 

# PLOTS

## DATA

### Subfield x Data Score

```{r echo=FALSE}
data_subfield_descriptives <- dates %>%
  group_by(subfield_groups) %>%
  summarise(mean_data_score = mean(open_data_score, na.rm = TRUE),
            SD = sd(open_data_score, na.rm = TRUE),
            N = n(),
            stderr = SD/sqrt(N))

data_subfield_descriptives$subfield_groups <- fct_relevel(data_subfield_descriptives$subfield_groups, c("Development", "Social", "Cognition", "Other"))

data_subfield_descriptives

# Specifying which levels of the subfield variable the significance bars need to compare
d1_comparisons <- list(c("Development", "Social"), c("Development", "Cognition"),  c("Development", "Other") )

# Plot

d1 <- data_subfield_descriptives %>%
  ggplot(aes(x = reorder(subfield_groups, mean_data_score), y = mean_data_score, fill = subfield_groups)) +
  geom_col() +
  geom_errorbar(aes(ymin = mean_data_score - stderr, ymax = mean_data_score + stderr), # specifying what the standard error is
                size=.3, # thinner lines
                width=.2) + # narrower bars
    theme_classic() +
    scale_x_discrete(limits=c("Development", "Social", "Cognition", "Other")) +
    scale_fill_manual(values=c("#EC407A","#42A5F5", "#FFCC33", "#00CC99")) +
  scale_y_continuous(limits = c(0,25), expand = c(0,0)) + # getting the bars to start at the bottom of the graph
  easy_remove_legend() +
  easy_all_text_size(size = 8) + # change the size of the text
  easy_labs(x = "Subfield", y = "Mean Open Data Score") + # change the x and y labels
  ggtitle('(a)') + 
  geom_signif(comparisons = d1_comparisons, y_position = c(10, 14, 18), tip_length = 0.1, annotation = c("n.s.", "*", "n.s."), textsize = 3.5, vjust = -0.3) # adding significance bars


```

### Time Period x Data Score

```{r echo=FALSE}
data_timeperiod_descriptives <- dates %>%
  group_by(time_period) %>%
  summarise(mean_data_score = mean(open_data_score, na.rm = TRUE),
            SD = sd(open_data_score, na.rm = TRUE),
            N = n(),
            stderr = SD/sqrt(N))

data_timeperiod_descriptives

# Specifying which levels of the time variable the significance bars need to compare
d2_comparisons <- list( c("2014-15", "2019-20"))

# Plot

d2 <- data_timeperiod_descriptives %>%
  ggplot(aes(x = time_period, y = mean_data_score, fill = time_period)) +
  geom_col() +
  geom_errorbar(aes(ymin = mean_data_score - stderr, ymax = mean_data_score + stderr), # specifying what the standard error is
                size=.3, # thinner lines
                width=.2) + # narrower bars
    theme_classic() +
    scale_fill_manual(values=c("#FFCCCC","#FF6666")) +
  scale_y_continuous(limits = c(0,25), expand = c(0,0)) + # getting the bars to start at the bottom of the graph
  easy_remove_legend() +
  easy_all_text_size(size = 8) + # change the size of the text
  easy_labs(x = "Time Period", y = "Mean Open Data Score") + # change the x and y labels
  ggtitle('(b)') +
  geom_signif(comparisons = d2_comparisons, y_position = 17, tip_length = 0.1,  annotation = "*", textsize = 3.5, vjust = -0.3) # adding significance bars


```

### Interaction between time and subfield - Data scores 

```{r echo=FALSE, message=FALSE, warning=FALSE}
data_subfieldtime_descriptives <- dates %>%
  group_by(subfield_groups, time_period) %>%
  summarise(mean_data_score = mean(open_data_score, na.rm = TRUE),
            SD = sd(open_data_score, na.rm = TRUE),
            N = n(),
            stderr = SD/sqrt(N))

data_subfieldtime_descriptives 

# Plot

d3 <- data_subfieldtime_descriptives  %>%
  ggplot(aes(x = subfield_groups, y = mean_data_score, fill = time_period)) +
  geom_col(position = "dodge") +
  geom_errorbar(aes(ymin = mean_data_score - stderr, ymax = mean_data_score + stderr), # specifying what the standard error is
                size=.3, # thinner lines
                width=.2, # narrower bars
                position=position_dodge(.9)) + 
    theme_classic() +
    scale_fill_manual(values=c("#FFCCCC","#FF6666")) +
  scale_y_continuous(limits = c(0,25), expand = c(0,0)) + # getting the bars to start at the bottom of the graph
  easy_all_text_size(size = 9) + # change the size of the text
  easy_labs(x = "Subfield", y = "Mean Open Data Score") + # change the x and y labels
  theme(legend.title = element_blank()) + # remove legend title
  ggtitle('(c)')

(d1 | d2) / d3

```

## MATERIALS

### Subfield x Materials Score

```{r echo=FALSE}
materials_subfield_descriptives <- dates %>%
  group_by(subfield_groups) %>%
  summarise(mean_materials_score = mean(open_materials_score, na.rm = TRUE),
            SD = sd(open_materials_score, na.rm = TRUE),
            N = n(),
            stderr = SD/sqrt(N))

materials_subfield_descriptives

# Specifying which levels of the subfield variable the significance bars need to compare
m1_comparisons <- list(c("Development", "Social"), c("Development", "Cognition"),  c("Development", "Other") )

# Plot

m1 <- materials_subfield_descriptives %>%
  ggplot(aes(x = subfield_groups, y = mean_materials_score, fill = subfield_groups)) +
  geom_col() +
  geom_errorbar(aes(ymin = mean_materials_score - stderr, ymax = mean_materials_score + stderr), # specifying what the standard error is
                size=.3, # thinner lines
                width=.2) + # narrower bars
    theme_classic() +
    scale_fill_manual(values=c("#EC407A","#42A5F5", "#FFCC33", "#00CC99")) +
  scale_y_continuous(limits = c(0,19), expand = c(0,0)) + # getting the bars to start at the bottom of the graph
  easy_remove_legend() +
  easy_all_text_size(size = 8) + # change the size of the text
  easy_labs(x = "Subfield", y = "Mean Open Materials Score") + # change the x and y labels
  ggtitle('(a)') + 
  geom_signif(comparisons = m1_comparisons, y_position = c(7.5, 10.5, 13.5), tip_length = 0.1, annotation = c("*", "*", "n.s."), textsize = 3.5, vjust = -0.3) # adding significance bars

```

### Time Period x Materials Score

```{r echo=FALSE}
materials_timeperiod_descriptives <- dates %>%
  group_by(time_period) %>%
  summarise(mean_materials_score = mean(open_materials_score, na.rm = TRUE),
            SD = sd(open_materials_score, na.rm = TRUE),
            N = n(),
            stderr = SD/sqrt(N))

materials_timeperiod_descriptives

# Specifying which levels of the time variable the significance bars need to compare
m2_comparisons <- list( c("2014-15", "2019-20"))

# Plot

m2 <- materials_timeperiod_descriptives %>%
  ggplot(aes(x = time_period, y = mean_materials_score, fill = time_period)) +
  geom_col() +
  geom_errorbar(aes(ymin = mean_materials_score - stderr, ymax = mean_materials_score + stderr), # specifying what the standard error is
                size=.3, # thinner lines
                width=.2) + # narrower bars
    theme_classic() +
    scale_fill_manual(values=c("#FFCCCC","#FF6666")) +
  scale_y_continuous(limits = c(0,19), expand = c(0,0)) + # getting the bars to start at the bottom of the graph
  easy_remove_legend() +
  easy_all_text_size(size = 8) + # change the size of the text
  easy_labs(x = "Time Period", y = "Mean Open Materials Score") + # change the x and y labels
  ggtitle('(b)') +
  geom_signif(comparisons = m2_comparisons, y_position = 11, tip_length = 0.1,  annotation = "*", textsize = 3.5, vjust = -0.3) # adding significance bars

```

### Interaction between time and subfield - Materials Score

```{r echo=FALSE, message=FALSE, warning=FALSE}
materials_subfieldtime_descriptives <- dates %>%
  group_by(subfield_groups, time_period) %>%
  summarise(mean_materials_score = mean(open_materials_score, na.rm = TRUE),
            SD = sd(open_materials_score, na.rm = TRUE),
            N = n(),
            stderr = SD/sqrt(N))

materials_subfieldtime_descriptives

# Plot

m3 <- materials_subfieldtime_descriptives  %>%
  ggplot(aes(x = subfield_groups, y = mean_materials_score, fill = time_period)) +
  geom_col(position = "dodge") +
  geom_errorbar(aes(ymin = mean_materials_score - stderr, ymax = mean_materials_score + stderr), # specifying what the standard error is
                size=.3, # thinner lines
                width=.2, # narrower bars
                position=position_dodge(.9)) + 
    theme_classic() +
    scale_fill_manual(values=c("#FFCCCC","#FF6666")) +
  scale_y_continuous(limits = c(0,19), expand = c(0,0)) + # getting the bars to start at the bottom of the graph
  easy_all_text_size(size = 9) + # change the size of the text
  easy_labs(x = "Subfield", y = "Mean Open Materials Score") + # change the x and y labels
    theme(legend.title = element_blank()) + # remove legend title
  ggtitle('(c)')

(m1 | m2) / m3

```

# SUBFIELD T-TESTS

## DATA

### Development vs. Cognition

```{r echo=FALSE}
devcog_data <- dates %>%
  filter(subfield_groups %in% c("Development", "Cognition"))

ttest1 <- t_test(open_data_score ~ subfield_groups, devcog_data, paired = FALSE)

report(ttest1)
```

### Development vs. Social

```{r echo=FALSE}
devsocial_data <- dates %>%
  filter(subfield_groups %in% c("Development", "Social"))

ttest2 <- t_test(open_data_score ~ subfield_groups, devsocial_data, paired = FALSE)

report(ttest2)
```

### Development vs. Other

```{r echo=FALSE}
devother_data <- dates %>%
  filter(subfield_groups %in% c("Development", "Other"))

ttest3 <- t_test(open_data_score ~ subfield_groups, devother_data, paired = FALSE)

report(ttest3)
```

## MATERIAL

### Developmental vs. Cognition

```{r echo=FALSE}
devcog_materials <- dates %>%
  filter(subfield_groups %in% c("Development", "Cognition"))

ttest4 <- t_test(open_materials_score ~ subfield_groups, devcog_materials, paired = FALSE)

report(ttest4)
```


### Developmental vs. Social

```{r echo=FALSE}
devsocial_materials <- dates %>%
  filter(subfield_groups %in% c("Development", "Social"))

ttest5 <- t_test(open_materials_score ~ subfield_groups, devsocial_materials, paired = FALSE)

report(ttest5)
```

### Developmental vs. Other

```{r echo=FALSE}
devother_materials <- dates %>%
  filter(subfield_groups %in% c("Development", "Other"))

ttest6 <- t_test(open_materials_score ~ subfield_groups, devother_materials, paired = FALSE)

report(ttest6)
```

## TIME T-TESTS

### DATA

```{r echo=FALSE}

ttest7 <- t_test(open_data_score ~ time_period, dates, paired = FALSE)

report(ttest7) 
```

### MATERIALS

```{r echo=FALSE}

ttest8 <- t_test(open_materials_score ~ time_period, dates, paired = FALSE)

report(ttest8) 
```